The bhsdtr package: flexible bayesian inference for hierarchical or non-hierarchical equal variance normal Signal Detection Theory models with or without ratings.

### 2017-11-03 inst/preprint/luxsdt.tex
black and white option in plot_sdt_fit

Fleming's \citeyear{hmetad} HMeta-d' model is a hierarchical version
of the meta-d' model \cite{maniscalco2012signal}, which in turn is a
generalization of the SDT model with additional criteria that allows
for a separate "meta-sensitivity" to account for possible
discrepancies between binary stimulus classification (referred to as
type 1 task) and a rating task (referred to as type 2 or
meta-cognitive task). We consider HMeta-d' here because it reduces to
the SDT model with ratings when type 1 and type 2 sensitivities are
equal. In HMeta-d' evidence distributions are normal with equal
variance. Normally distributed random effects of one factor are
allowed for sensitivities and parameters indirectly representing the
criteria, for lack of a better name from now on referred to as raw
criteria. The actual criteria are subject-specific sorted values of
unconstrained raw criteria and it is these unconstrained parameters,
not the actual criteria, that are given independent hierarchical
normal distributions representing variability due to subjects. Since
sorting is not injective the space of raw criteria is not isomorphic
to the space of actual criteria and each element of the raw criteria
vector can represent a value of any criterion, depending on the values
of other elements of the raw criteria vector. The model does not
account for possible correlations between random
effects. Sensitivities are represented as unrestricted scalars even
though they are non-negative by definition. Out of the box the code
provided by the author allows only for a very limited regression
structure to be placed on SDT parameters. Software implementation
relies on ready-made model specifications expressed in JAGS language
that are aimed at several simple types of experimental design (e.g.,
single subject or single group of subjects). The models can be fitted
using convenient MATLAB functions.

>>>>

Fleming's \citeyear{hmetad} HMeta-d' model is a hierarchical version
of the meta-d' model \cite{maniscalco2012signal}, which in turn is a
generalization of the SDT model with additional criteria that allows
for a separate "meta-sensitivity" to account for possible
discrepancies between binary stimulus classification (referred to as
type 1 task) and a rating task (referred to as type 2 or
meta-cognitive task). We consider HMeta-d' here because it reduces to
the SDT model with ratings when type 1 and type 2 sensitivities are
equal. In HMeta-d' evidence distributions are normal with equal
variance. Normally distributed random effects of one factor are
allowed for sensitivities and for parameters indirectly representing
the criteria, for lack of a better name from now on referred to as raw
criteria. The actual criteria are subject-specific sorted values of
unconstrained raw criteria and it is these unconstrained parameters,
not the actual criteria, that are given independent hierarchical
normal distributions representing variability due to subjects. Since
sorting is not injective the space of raw criteria is not isomorphic
to the space of actual criteria and each element of the raw criteria
vector can represent a value of any criterion, depending on the values
of other elements of the raw criteria vector. The model does not
account for possible correlations between random
effects. Sensitivities are represented as unrestricted scalars even
though they are non-negative by definition. Out of the box the code
provided by the author allows only for a very limited regression
structure to be placed on SDT parameters.
% Software implementation relies on ready-made model specifications
% expressed in JAGS language that are aimed at several simple types of
% experimental design (e.g., single subject or single group of
% subjects). The models can be fitted using convenient MATLAB
% functions.
